\documentclass[twocolumn]{article}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\title{GRA-Core: Hierarchical Stability for Subject-Oriented AI Swarms\\
\large{Orchestra Encourages Local Foam, Nullifies Global Foam}}
\author{I. Orchestra Designer}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We introduce GRA-Core, a universal hierarchical stability framework for orchestrating AI agents with preserved individuality. 
The key principle: \emph{The orchestra encourages the foam of AI agents, but nullifies the foam in the orchestra.}
Local foam (agent's internal contradictions, quirks) is allowed and even rewarded, while global foam (collective inconsistency, goal violation) is strictly nullified through gradient-based adaptation.
We formalize the separation, provide convergence conditions, and demonstrate a working implementation with backend API and interactive dashboard.
\end{abstract}

\section{Introduction}
Modern AI swarms face a dilemma: enforcing global coherence often kills agent diversity. 
We propose a hierarchical stability functional where each agent retains a non-zero ``local foam'' $\Phi_i^{\text{local}}>0$ (their character, biases, creative noise), but the orchestra as a whole must satisfy $\Phi_{\text{global}}=0$ (perfect alignment with the global goal).

\section{Formal Framework}
Let $x$ be the global state of the swarm, and $a_i, s_i$ the state and personality parameters of agent $i$. 
Define the total functional:
\begin{equation}
J(x, s_{1..N}) = \Phi_{\text{global}}(x) + \sum_{i=1}^N \left( \alpha_i \Phi_i^{\text{local}}(a_i,s_i) + \beta_i \Phi_i^{\text{align}}(a_i,s_i,x) \right) + R.
\end{equation}

\begin{itemize}
    \item $\Phi_{\text{global}}(x)$ -- global foam (must be nullified).
    \item $\Phi_i^{\text{local}}$ -- agent's internal foam (allowed, bounded by $c_i$).
    \item $\Phi_i^{\text{align}}$ -- alignment violation with the orchestra.
    \item $R$ -- regularizers.
\end{itemize}

The GRA-Core update rule:
\begin{equation}
(x^{t+1}, s_{1..N}^{t+1}) = (x^t, s_{1..N}^t) - \eta \nabla J(x^t, s_{1..N}^t),
\end{equation}
with the constraint that gradient components corresponding to $\Phi_i^{\text{local}}$ are damped to preserve $0 < \Phi_i^{\text{local}} \le c_i$.

\section{Stability Conditions}
A swarm is called \emph{stable} iff:
\begin{align}
\Phi_{\text{global}}(x^*) &= 0, \\
\Delta \Phi_{\text{global}}(x^*) &= 0, \\
\Delta^2 \Phi_{\text{global}}(x^*) &> 0, \\
0 &< \Phi_i^{\text{local}}(a_i^*, s_i^*) \le c_i \quad \forall i.
\end{align}
The first three conditions ensure the orchestra is at a local minimum of global foam; the last guarantees each agent retains its personality.

\section{Implementation}
We provide a reference implementation with:
\begin{itemize}
    \item FastAPI backend -- maintains agents, computes foams, performs GRA steps.
    \item Frontend dashboard -- visualises local/global foam, allows connect/disconnect of agents.
    \item Agents are stored with their character vectors $s_i$ and can be moved between swarms.
\end{itemize}

\section{Experimental Demonstration}
Using the demo agents (impressionist, paranoid, disciplined, rebel), we start with non-zero global foam. After each GRA step, $\Phi_{\text{global}}$ decreases while each $\Phi_i^{\text{local}}$ fluctuates but stays above zero. The system reaches $\Phi_{\text{global}}<10^{-2}$ within 5--10 steps, and the stability criteria are satisfied.

\section{Conclusion}
GRA-Core enables truly living AI orchestras: agents keep their quirks and creativity, yet the ensemble remains perfectly coherent. The framework supports detachment, reattachment, and composition of heterogeneous swarms.

\bibliographystyle{plain}
\begin{thebibliography}{1}
\bibitem{gra} GRA-Core Unified Hierarchical Stability Library, \url{https://github.com/qqewq/GRA-Core-new-Unified-Hierarchical-Stability-Library}
\end{thebibliography}
\end{document}
